\pisodm: Building SOC Applications in the Presence of Non-Functional Requirements

### 2018-01-18 JournalPISODM2016/ProofJan2018/main.tex
corrected proof

%
\authorA{\sf Khalid Belhajjame}
\affA{Universit\'e de Paris - Dauphine -- Paris, France\\
  E-mail: kbelhajj@googlemail.com}

\authorB{\sf Valeria~de~Castro}
\affB{Universidad Rey Juan Carlos -- M\'{o}stoles, Spain\\
  E-mail: valeria.decastro@urjc.es}

\authorC{\sf Javier~A.~Espinosa-Oviedo}
\affC{Barcelona Supercomputing Center (BSC), Spain and\\
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico/France\\
  E-mail: javiera.espinosa@bsc.es}

\authorD{\sf Martin~A.~Musicante}
\affD{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
  E-mail: mam@dimap.ufrn.br}

\authorE{\sf Umberto~Souza~da~Costa}
\affE{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
  E-mail: umberto@dimap.ufrn.br}

\authorF{\sf Pl\'acido~A.~Souza~Neto}
\affF{Instituto Federal de Educa\c{c}\~{a}o, Ci\^{e}ncia e Tecnologia do Rio Grande do Norte -- Natal, Brazil\\
  E-mail: placido.neto@ifrn.edu.br}

\authorG{\sf Genoveva~Vargas-Solar}
\affG{Univ. Grenoble Alpes, CNRS, Institute of Engineering Univ. Grenoble Alpes (Grenoble INP), LIG, 38000 Grenoble, France and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico/France
	\\
  E-mail: genoveva.vargas@imag.fr}

\authorH{\sf Jos\'e-Luis~Zechinelli-Martini}
\affH{Universidad de las Am\'ericas-Puebla -- Cholula, Mexico and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Mexico/France\\
  E-mail: joseluis.zechinelli@udlap.mx}

@@

\noindent Jos\'e-Luis~Zechinelli-Martini is titular professor of the Department of Computing, Electronics and Mecatronics at the Universidad de las Américas Puebla (UDLAP) since 2002 and he is currently senior researcher at LAFMIA. He is head of the Data and Knowledge Management Group (DBKM) of LAFMIA. In 2001 he obtained his Ph.D. in Computer Science and in 1997 he obtained his Master Degree in Computer Science at University Joseph Fourier, Grenoble, France. In 1993 he obtained his diploma on Computer Systems Engineering at UDLAP. Between 2003 and 2006 he was director of the CENTIA and head of the PhD program on Computer Science. His research project concerns on the integration of Big Data collections on different infrastructures and the specification of spatio-temporal and visualization query languages for retrieving multimedia and multiform data from distributed services.
\end{bio}

>>>>

%
\authorA{\sf Khalid Belhajjame}
\affA{University Paris-Dauphine, PSL Research University, \\
CNRS, UMR 7243, Centre Lamsade, 75016 Paris, France\\
  E-mail: kbelhajj@googlemail.com}

\authorB{\sf Valeria~de~Castro}
\affB{Kybele Research Group, Rey Juan Carlos University, Madrid, Spain\\
  E-mail: valeria.decastro@urjc.es}

\authorC{\sf Javier~A.~Espinosa-Oviedo}
\affC{Barcelona Supercomputing Center (BSC), Barcelona, Spain
 and French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Puebla, Mexico/ Grenoble, France\\
  E-mail: javiera.espinosa@bsc.es}

\authorD{\sf Martin A. Musicante and \\ Umberto Souza da Costa}
\affD{Department of Computer Science (DIMAp), \\ 
Federal University of Rio Grande do Norte, Natal, Brazil\\
  E-mail: mam@dimap.ufrn.br\\
  E-mail: umberto@dimap.ufrn.br}

%\authorE{\sf Umberto~Souza~da~Costa}
%\affE{Universidade Federal do Rio Grande do Norte -- Natal, Brazil\\
%  E-mail: umberto@dimap.ufrn.br}

\authorE{\sf Pl\'acido~A.~Souza~Neto$^*$}
\affE{Federal Institute for Education, Science and Technology \\
of Rio Grande do Norte, Natal, Brazil\\
  E-mail: placido.neto@ifrn.edu.br\\
  *Corresponding author}

\authorF{\sf Genoveva~Vargas-Solar}
\affF{Univ. Grenoble Alpes, CNRS, Institute of Engineering Univ. Grenoble Alpes (Grenoble INP), LIG, 38000 Grenoble, France and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Puebla, Mexico/ Grenoble, France
	\\
  E-mail: genoveva.vargas@imag.fr}

\authorG{\sf Jos\'e-Luis~Zechinelli-Martini}
\affG{University of the Americas-Puebla, Cholula, Mexico and
	French-Mexican Laboratory of Informatics and Automatic Control (LAFMIA), Puebla, Mexico/ Grenoble, France\\
  E-mail: joseluis.zechinelli@udlap.mx}

@@

\noindent Jos\'e-Luis~Zechinelli-Martini is titular professor of the Department of Computing, Electronics and Mecatronics at the Universidad de las Américas Puebla (UDLAP) since 2002 and he is currently senior researcher at LAFMIA. He is head of the Data and Knowledge Management Group (DBKM) of LAFMIA. In 2001 he obtained his Ph.D. in Computer Science and in 1997 he obtained his Master Degree in Computer Science at University Joseph Fourier, Grenoble, France. In 1993 he obtained his diploma on Computer Systems Engineering at UDLAP. Between 2003 and 2006 he was director of the CENTIA and head of the PhD program on Computer Science. His research project concerns on the integration of Big Data collections on different infrastructures and the specification of spatio-temporal and visualization query languages for retrieving multimedia and multiform data from distributed services.

\bigskip

\noindent This paper is a revised and expanded version of a paper entitled ``Supporting Non-functional Requirements in Services Software Development Process: An MDD Approach'' presented at SOFSEM 2014, Nov\'y Smokovec, High Tatras, Slovakia, January 25-30, 2014~\cite{Placido2014}.
\end{bio}
